Proposed Solution

### 2016-11-14 Ennan-Proposal/travis.tex
autocommit

\begin{figure}[!tbh]
  \centering
  \begin{tikzpicture}
    \draw (0,0) rectangle (6,4); 
    \node [align=left] at (1.5,3.2) {\footnotesize \textbf{Breaking Rules}: \\ \footnotesize node\_js $\le$ 0 \\ \footnotesize \ldots};
    \draw (1.5,0.2) rectangle (5,2.2);
    \node [align=left] at (3,1.3) {\footnotesize \textbf{Necessary Rules}: \\ \footnotesize node\_js $\ge$ 0.4 \\ \footnotesize \ldots};
  \end{tikzpicture}
  \caption{An example set of necessary and breaking rules if we have seen a failing file with {\footnotesize node\_js: 0}, and a passing file with {\footnotesize node\_js: 0.4.}}
  \label{fig:versionSL}
\end{figure}

>>>>

\begin{figure}[!tbh]
  \centering
  \begin{tikzpicture}
    \draw (0,0) rectangle (6,3.7); 
    \node [align=left] at (1.5,2.9) {\footnotesize \textbf{Breaking Rules}: \\ \footnotesize node\_js $\le$ 0 \\ \footnotesize \ldots};
    \draw (1.6,0.2) rectangle (5,2.2);
    \node [align=left] at (3.3,1.3) {\footnotesize \textbf{Necessary Rules}: \\ \footnotesize node\_js $\ge$ 0.4 \\ \footnotesize \ldots};
  \end{tikzpicture}
  \caption{An example set of necessary and breaking rules if we have seen a failing file with {\footnotesize node\_js: 0}, and a passing file with {\footnotesize node\_js: 0.4.}}
  \label{fig:versionSL}
\end{figure}
